Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-01-08 main.tex
wip

A {\em contour}
$\contour \in (\WORDS \cup \REGS \cup \{\PCname\}) \rightarrow \{\HIGH,\LOW\}$ is a
map from machine components to ``security levels,'' where $\HIGH$ marks
locations containing secret or low-integrity data and $\LOW$ marks those
with public or high-integrity data.

@@

\begin{itemize}
\item
  Idea of accessibility: set of data memory addresses that can legally be read or written at a particular execution point.
  (Assume instruction memory is distinct.)
\item
  Stack protection intuition in a nutshell: caller's memory data is not accessible to callee, although callee's memory data is accessible to caller.
  This gives both an integrity property (callee cannot affect caller's memory) and a secrecy property
  (caller's memory cannot affect callee).
  Can generalize to other control situations, such as coroutines, threads, compartments,...
\item
  In NI terms, protected programs are oblivious to variations in memory outside of their accessible set.
  Unlike standard NI, the accessible set changes dynamically, so we cannot just frame the property in terms of
  variant start states. [Is this true? Is it a significant difference? Are there other significant differences?]
\item
  We start with a very simple (and unrealistic) set of assumptions/conventions for stack frames and procedure calls:
  \begin {itemize}
  \item Memory is divided into an instruction region and a data region. The data region contains a single contiguous stack, divided into frames, each associated with a procedure activation. (The stack grows in the direction of increasing addresses.)
  \item Each frame consists of a saved return address and a single word of local data. These [both??] form the entirety of the procedure's memory data, and are the only thing we need to track when considering accessibility.
  \item Registers other than RA, SP are not affected by calls or returns and hence are the (only) way to pass values between caller and callee.
  \item Instructions serving as calls are statically marked as such in the code. [The entry and exit sequences must also be marked???]
  \item The code for each procedure is bracketed by fixed entry and exit sequences (details to follow), which save/restore the RA and
    adjust the SP. [Are these assumptions or checked facts?]
  \item During the body of the procedure, the single word of local data is accessed via SP, which does not change (except during a call, of course).  The stored RA in the frame never changes. [I'm confused about these. They are checked facts, not assumptions.]
  \end {itemize}
  In this model, the definition of accessible memory is simply all (data) memory at addresses $\geq pc$.
\item
  Describe conjecture 2 property in terms of this model: informally and formally.
\item
  Define abstract state descriptions.
\item
  Define step consistency.
\item
  Discuss relationship between state consistency and conjecture 2 property.  (Former is: presumably stronger; hopefully not
  too strong that it produces lots of undesired test failures; surely easier to test).

>>>>

A {\em contour}
$\contour \in \CONTOURS = (\WORDS \cup \REGS \cup \{\PCname\}) \rightarrow \{\HIGH,\LOW\}$ is a
map from machine components to ``security levels,'' where $\HIGH$ marks
locations containing secret or low-integrity data and $\LOW$ marks those
with public or high-integrity data.

@@

\begin{itemize}
\item
  Idea of accessibility: set of data memory addresses that can legally be read or written at a particular execution point.
  (Assume instruction memory is distinct.)
\item
  Stack protection intuition in a nutshell: caller's memory data is not accessible to callee, although callee's memory data is accessible to caller.
  This gives both an integrity property (callee cannot affect caller's memory) and a secrecy property
  (caller's memory cannot affect callee).
  Can generalize to other control situations, such as coroutines, threads, compartments,...
\item
  In NI terms, protected programs are oblivious to variations in memory outside of their accessible set.
  Unlike standard NI, the accessible set changes dynamically, so we cannot just frame the property in terms of
  variant start states. [Is this true? Is it a significant difference? Are there other significant differences?]
\end{itemize}

We start with a very simple (and unrealistic) set of assumptions/conventions for stack frames and procedure calls.
We assume that memory is divided into two disjoint regions, one containing the code, the other the stack.
Code begins at address 0; the stack begins at address $B$ and grows in the direction of increasing addresses.

The part of the stack between $B$ and the stack pointer \textsc{sp} is structured into a sequence of consecutive
\emph{frames}. Each frame consists of a single return address and a single word of local data.

  \begin {itemize}
  \item Memory is divided into an instruction region and a data region. The data region contains a single contiguous stack, divided into frames, each associated with a procedure activation. (The stack grows in the direction of increasing addresses.)
  \item Each frame consists of a saved return address and a single word of local data. These [both??] form the entirety of the procedure's memory data, and are the only thing we need to track when considering accessibility.
  \item Registers other than RA, SP are not affected by calls or returns and hence are the (only) way to pass values between caller and callee.
  \item Instructions serving as calls are statically marked as such in the code. [The entry and exit sequences must also be marked???]
  \item The code for each procedure is bracketed by fixed entry and exit sequences (details to follow), which save/restore the RA and
    adjust the SP. [Are these assumptions or checked facts?]
  \item During the body of the procedure, the single word of local data is accessed via SP, which does not change (except during a call, of course).  The stored RA in the frame never changes. [I'm confused about these. They are checked facts, not assumptions.]
  \end {itemize}
  In this model, the definition of accessible memory is simply all (data) memory at addresses $\geq pc$.
\begin{itemize}
\item
  Describe conjecture 2 property in terms of this model: informally and formally.
\item
  Define abstract state descriptions.
\item
  Define step consistency.
\item
  Discuss relationship between state consistency and conjecture 2 property.  (Former is: presumably stronger; hopefully not
  too strong that it produces lots of undesired test failures; surely easier to test).
